Making Sequential Programs Deterministic

### 2019-04-05 java-design.tex
Edits on page 15

The return type of \<System.getenv>, which reads an operating system
environment variable, is always \<NonDet>.
The return type of \codeid{System.getProperty} is usually \<NonDet>. However,
the result is \<Det> if the argument is \codeid{"line.separator"}; although
it varies by operating system, many programs including \<diff> hide those
differences from the user.
The result is also deterministic for \codeid{"path.separator"} and
\codeid{"file.separator"}, because these lead to the same behavior given
corresponding environments.
The user can specify input properties that must be passed on the \<java>
command line and thus act like inputs to the program; these are also
treated as deterministic.
The inputs to a program are also treated as \<Det>.  That is, the parameter
type of the \<main> method is implicitly annotated as
\<@Det String @Det []>, a deterministic array of deterministic strings.

>>>>

The return type of \<System.getenv>, which reads an operating system
environment variable, is always \<@NonDet>.

The return type of \codeid{System.getProperty} is usually \<@NonDet>. However,
the result is \<@Det> if the argument is \codeid{"line.separator"}; although
it varies by operating system, many programs including \<diff> and editors hide those
differences from the user.
The result is also deterministic for \codeid{"path.separator"} and
\codeid{"file.separator"}, because these lead to the same behavior given
corresponding environments.
The user can specify input properties that must be passed on the \<java>
command line and thus act like inputs to the program; these are also
treated as deterministic.

The inputs to a program are also treated as \<Det>.  That is, the type of
the formal parameter to \<main> is
\<@Det String @Det []>, a deterministic array of deterministic strings.

### 2019-04-05 randoop-case-study.tex
randoop bugs
Edits on page 15

To evaluate the usability of \theDeterminismChecker,
we applied it to the Randoop test
generation tool~\ifanonymous\citepalias{randoop-tool}\else\cite{PachecoLEB2007}\fi.
We also wrote specifications for libraries it uses, such as the JDK, JUnit,
and others.
Like \theDeterminismCheckerImplementation,
all the case study materials are publicly available at \myurl{\todo{url for
    case study}} for reproducibility.

@@

\item \bugTimestampOutput:
  Diagnostic output printed a timestamp.
  The developers fixed it by making it obeyed an
  option about whether to print timestamps (commit a460df97).
  The developers may not have noticed this because their log-postprocessing
  tools removed them from the log when doing comparisons.

>>>>

To evaluate the usability of \theDeterminismChecker,
we applied it to the Randoop test
generator~\ifanonymous\citepalias{randoop-tool}\else\cite{PachecoLEB2007}\fi.
We also wrote specifications for libraries Randoop uses, such as the JDK, JUnit,
and others.
Like \theDeterminismCheckerImplementation,
all the case study materials are publicly available at \myurl{\todo{url for
    case study}} for reproducibility.

@@

\item \bugTimestampOutput:
  Diagnostic output printed a timestamp.
  The developers fixed it by making it obey an
  option about whether to print timestamps (commit a460df97).
  The developers may not have noticed this because their log-postprocessing
  tools removed them from the log when doing comparisons.
